### 2025-03-26 sup/sup.tex
clean

\begin{longtable*}[t]{ccccc}
\toprule
No. & LastName & FirstName & DatasetID & Dataset\\
\midrule
1 & Cornelissen & Johannes & 37 & Sheffield Database\\
2 & Swaine & Emily & 51 & Tropical Plant Traits From Borneo Database\\
3 & Kleyer & Michael & 25 & The LEDA Traitbase\\
4 & Cornwell & Will & 55 & Jasper Ridge Californian Woody Plants Database\\
5 & Lloyd & Jon & 34 & The RAINFOR Plant Trait Database\\
\bottomrule
\end{longtable*}
\endgroup{}

>>>>

\begin{longtable*}[t]{ccccc}
\toprule
No. & LastName & FirstName & DatasetID & Dataset\\
\midrule
1 & Cornelissen & Johannes & 37 & Sheffield Database\\
2 & Swaine & Emily & 51 & Tropical Plant Traits From Borneo Database\\
3 & Kleyer & Michael & 25 & The LEDA Traitbase\\
4 & Cornwell & Will & 55 & Jasper Ridge Californian Woody Plants Database\\
5 & Lloyd & Jon & 34 & The RAINFOR Plant Trait Database\\
\addlinespace
6 & Zanne & Amy & 61 & Global Wood Density Database\\
7 & Weiher & Evan & 66 & Midwestern and Southern US Herbaceous Species Trait Database\\
8 & Cornelissen & Johannes & 72 & Sheffield \& Spain Woody Database\\
9 & Bond & William & 47 & South African Woody Plants Database (ZLTP)\\
10 & Ordonez & Jenny & 88 & The Netherlands Plant Traits Database\\
\addlinespace
11 & Peuelas & Josep & 91 & Catalonian Mediterranean Forest Trait Database\\
12 & Reich & Peter & 94 & Global A, N, P, SLA Database\\
13 & Sosinski & Enio & 77 & FAPESP Brazil Rainforest Database\\
14 & van Bodegom & Peter & 90 & Ukraine Wetlands Plant Traits Database\\
15 & Wright & S. Joseph & 112 & Panama Plant Traits Database\\
\addlinespace
16 & Anand & Madhur & 100 & Plant Traits in Pollution Gradients Database\\
17 & Wright & Ian & 64 & Neotropical Plant Traits Database\\
18 & Poorter & Lourens & 33 & Tropical Rainforest Traits Database\\
19 & Finegan & Bryan & 74 & Costa Rica Rainforest Trees Database\\
20 & Laughlin & Daniel & 193 & Plant Traits for Pinus and Juniperus Forests in Arizona\\
\addlinespace
21 & Kramer & Koen & 191 & Baccara - Plant Traits of European Forests\\
22 & Jansen & Steven & 241 & Xylem Functional Traits (XFT) Database\\
23 & Craven & Dylan & 230 & Panama Tree Traits\\
24 & Gutierrez & Alvaro G. & 123 & VirtualForests Trait Database\\
25 & Powers & Jennifer & 263 & Costa Rican Tropical Dry Forest Trees\\
\addlinespace
26 & Gross & Nicolas & 275 & Plant Traits From Spanish Mediteranean shrublands\\
27 & Wirth & Christian & 68 & The Functional Ecology of Trees (FET) Database  - Jena\\
28 & Adler & Peter & 285 & Functional traits explaining variation in plant life history strategies\\
29 & Higuchi & Pedro & 305 & Araucaria Forest Database\\
30 & Holl & Karen & 306 & Plant traits from Costa Rica\\
\addlinespace
31 & Mazzochini & Guilherme & 357 & Functional traits of woody species in the Brazilian semi-arid region\\
32 & van Bodegom & Peter & 330 & Traits of Ukraine native and invasive plant species\\
33 & Swenson & Nathan & 288 & CTFS Luquillo Forest Dynamics Plot\\
34 & Weigelt & Alexandra & 347 & Traits of 59 grassland species\\
35 & Hietz & Peter & 384 & Panama wood anatomy\\
\addlinespace
36 & Chacon & Eduardo & 377 & Functional Traits of Trees in Golfo Dulce, Costa Rica\\
37 & Rolo Romero & Victor & 396 & Rehabilitating Coastal dune forest\\
38 & Li & Yuanzhi & 419 & Sherbrooke\\
39 & Boonman & Coline & 420 & Chinese savanna trees - aboveground trait data\\
40 & Jacobsen & Kim & 398 & Yangambi (DR Congo) tropical forest tree traits\\
\addlinespace
41 & Paine & C. E. Timothy & 439 & Functional Traits of Trees\\
42 & Lopez-Gonzalez & NA & 413 & Zanne et al. Global wood density database.\\
43 & Silva & Ana Carolina & 393 & LABDENDRO Brazilian Subtropical Forest Traits Database [Dataset II]\\
44 & Falster & Daniel & 431 & BAAD: a biomass and allometry database for woody plants\\
45 & Bjorkman & Anne & 468 & Tundra Trait Team\\
\addlinespace
46 & Thomas & Evert & 473 & Functional trait data Colombian dry Forest trees\\
47 & Pausas & Juli & 474 & BROT 2.0\\
48 & Torres-Ruiz & Jose M. & 492 & Torres-Ruiz\\
49 & Schmitt & Sylvain & 532 & UppangalaTraits\\
50 & Laughlin & Daniel & 538 & NZ tree traits\\
\addlinespace
51 & Michelaki & Chrysanthi & 539 & Thermo-Mediterranean species along Greece\\
52 & Richardson & Sarah & 572 & New Zealand Nothofagus leaf and stem traits\\
53 & Schrader & Julian & 587 & Raja Ampat tree dataset\\
54 & Apgaua & Deborah & 622 & Daintree Rainforest Functional Traits Data\\
55 & Tng & David & 625 & Tng et al 2013 Traits\\
\addlinespace
56 & Vasquez & Maribel & 627 & functional traits native and invasive species in tropical dry forest\\
57 & Aubin & Isabelle & 629 & Traits of Plants in Canada (TOPIC)\\
58 & Watkins & Harry & 630 & Watkins, Sjoman and Hitchmough CSR ordination of trees\\
59 & Bruy & David & 632 & Atractocarpus from new Caledonia\\
60 & Olson & Mark E. & 635 & Olson PNAS 2018\\
\addlinespace
61 & Boukili & Vanessa & 636 & La Selva FT Data\\
62 & Olson & Mark E. & 638 & Olson et al AnnBot 2018 Corners Rules\\
63 & VILLACIS & JAIME & 653 & RASGOS FUNCIONALES ESPECIES ARBOREAS CUENCA AMAZONICA\\
64 & Staples & Timothy & 674 & Staples et al Australian Reforestation Tree Database\\
65 & Helsen & Kenny & 706 & riparian forb traits W-Europe\\
\addlinespace
66 & Olson & Mark E. & 708 & Olson et al. 2020 Ecological Monographs vessel diameter-plant height scaling\\
67 & Thom & Dominik & 662 & Thom 2019\\
68 & McCarthy & James & 475 & Woody plant traits from southeast Queensland, Australia\\
69 & Fernndez-Mndez & Fernando & 668 & Traits of urban species from Ibagu Colombia\\
70 & Jansen & Steven & 673 & Wagenfhr Woodatlas\\
\addlinespace
71 & Scalon & Marina & 681 & Scalon bark traits\\
72 & Li & Yuanzhi & 744 & Heishiding\_Performance\_Trait\_Environment\_Data\\
\bottomrule
\end{longtable*}
\endgroup{}
